Plots_manuscript_v0.3

### 2020-07-30 R/Plots_manuscript_v0.3.Rmd
Finish drafting first Results section v0.3 comparing heritabilities and GxE

Add any libraries/scripts that need to be loaded for these analyses here.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
library(viridis)
library(lubridate)
library(switchgrassGWAS)
library(GGally)
source("~/Github/Functions_ggplot-theme-adjustments_2018-01-03.R")
```

# Load data
Add any data that needs to be loaded for these analyses here.
```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
metadata <- read_rds(file.path(workingdir, "data", "metadata.rds"))
sites <- read_rds(file.path(workingdir, "data", "sites.rds"))
subpops <- read_rds(file.path(workingdir, "data", "subpop_color_coding.rds"))
phe_gr_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_GR50.rds"))
phe_fl_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_FL50.rds"))
phenotypes <- readRDS("~/Github/pvdiv-phenology-gxe/data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
h2fl <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_FL50_related_functions_of_weather_v3.csv")
h2gr <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_GR50_related_functions_of_weather_v2.csv")
h2gr4 <- read_csv(file.path(workingdir, "analysis", "heritability", "h2_df_GR50_related_functions_of_weather_v4.csv"))
h2gr <- h2gr %>%
  full_join(h2gr4)
```

@@

# Heritability Plots

## h2 as functions of GR50 and FL50
```{r}
h2all <- h2fl %>%
  full_join(h2gr)

f1h2 <- h2all %>%
  filter(phe %in% c("FL50", "GR50")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "all",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "GR50" ~ "50% greenup",
                              phe == "FL50" ~ "50% flowering",
                              TRUE ~ phe))
f1h2$site <- factor(f1h2$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "all", "nine_sites"))
f1h2$phe_name <- factor(f1h2$phe_name, levels = c("50% greenup", "50% flowering"))
f1h2$subpop_name <- factor(f1h2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
ggh21 <- f1h2 %>%
  filter(!(site %in% c("nine_sites", "IL")) & !(subpop %in% c("three_subpops", "Atlantic"))) %>%
  ggplot(aes(x = site, y = Estimate)) +
  geom_bar(aes(fill = site == "all"), stat = "identity") +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  facet_grid(phe_name ~ subpop_name) +
  theme(panel.spacing.x = unit(0.1, 'cm'), 
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none") + 
  ylim(c(0, 1)) +
  xlab("Common Gardens") + 
  ylab(bquote('h'^2)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
  #
save_plot("../manuscript/plots/h2_GR_FL_site_by_subpop.png", plot = ggh21, base_height = 3.5, base_asp = 1.618)

f1h2 %>%
  filter(!(site %in% c("all", "nine_sites", "IL")) & !(subpop %in% c("three_subpops", "Atlantic"))) %>%
  ungroup() %>%
  group_by(phe) %>%
  summarise(mean = mean(Estimate))
f1h2 %>%
  filter((site %in% c("all")) & !(subpop %in% c("three_subpops", "Atlantic"))) %>%
  ungroup() %>%
  group_by(phe) %>%
  summarise(mean = mean(Estimate))
```

## h2 flowering weather
```{r}
flh2 <- h2fl %>%
  filter(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "FL50" ~ "50% flowering",
                              phe == "dyln_fl50" ~ "daylength",
                              phe == "dyln_change_sec" ~ "daylength change (s)",
                              phe == "cgdd_12c_gr2fl" ~ "GDD, GR to FL",
                              phe == "crain_gr2fl" ~ "Rainfall, GR to FL",
                              phe == "crain_1d" ~ "Rainfall, 1 day",
                              phe == "crain_2d" ~ "Rainfall, 2d sum",
                              phe == "crain_3d" ~ "Rainfall, 3d sum",
                              phe == "crain_5d" ~ "Rainfall, 5d sum",
                              phe == "crain_7d" ~ "Rainfall, 7d sum",
                              TRUE ~ phe))
flh2$site <- factor(flh2$site, levels = rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "nine_sites")))
flh2$phe_name <- factor(flh2$phe_name, levels = c("50% flowering", "daylength",
                                                  "daylength change (s)",
                                                  "GDD, GR to FL",
                                                  "Rainfall, GR to FL",
                                                  "Rainfall, 1 day",
                                                  #"Rainfall, 2d sum",
                                                  "Rainfall, 3d sum",
                                                  "Rainfall, 5d sum"#,
                                                  #"Rainfall, 7d sum"
                                                  ))
flh2$subpop_name <- factor(flh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
site_plot <- rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD", "All", "Texas", "North"))
subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))

save_plot("../manuscript/plots/h2_FL_site_weather_functions_All_Sites_v3.png", plot = flh2_p1, base_height = 7, base_asp = 1.1)

flh2_p2 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.45)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")

save_plot("../manuscript/plots/h2_FL_site_weather_functions_All_Sites_v2.png", plot = flh2_p2, base_height = 4, base_asp = 1.5)
```
## h2 greenup weather
```{r}
h2gr
```

subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))
i=3
subpop_v[[i]]
site_plot <- c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North")

grh2_p1 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v2.png", plot = grh2_p1, base_height = 7.5, base_asp = 1.1)

grh2_p2 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.5)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v3.png", plot = grh2_p2, base_height = 5, base_asp = 1.3)

grh2_p3 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.11)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v4.png", plot = grh2_p3, base_height = 4, base_asp = 1.5)

gr_fl_p1 <- plot_grid(grh2_p3, flh2_p2, nrow = 2)

save_plot("../manuscript/plots/h2_GR_and_FL_site_weather_functions_All_Sites.png", plot = gr_fl_p1, base_height = 4.6, base_asp = 1.35)
```
## Phenotype correlations
can you easily look at the correlation between greenup ranks at OK versus NE?
```{r}
phe_gr_df %>%
  filter(SITE %in% c("LINC", "STIL")) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, -PLOT_GL) %>%
  pivot_wider(names_from = "SITE", values_from = "GR50", values_fn = mean) %>%
  ggplot(aes(x = STIL, y = LINC)) +
  geom_hex() + #aes(color = SUBPOP), height = 1, width = 1) +
  scale_fill_viridis(option = "B",
                     end = 0.9, direction = -1)

@@

```{r}
pand <- cor_fl %>%
  filter(SUBPOP %in% c("Gulf")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = TRUE) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
pane <- cor_fl %>%
  filter(SUBPOP %in% c("Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = TRUE) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
panf <- cor_fl %>%
  filter(SUBPOP %in% c("Gulf", "Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = TRUE) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
pana <- cor_gr %>%
  filter(SUBPOP %in% c("Gulf")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = TRUE) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = c(0.4, 0.85))
panb <- cor_gr %>%
  filter(SUBPOP %in% c("Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = TRUE) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
panc <- cor_gr %>%
  filter(SUBPOP %in% c("Gulf", "Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = TRUE) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")

pheno_corr <- plot_grid(pana, panb, panc, pand, pane, panf, nrow = 2)
save_plot(filename = "../manuscript/plots/Phenotypic_correlations_GR50_FL50_2.png", plot = pheno_corr, base_height = 5)
```

>>>>

Add any libraries/scripts that need to be loaded for these analyses here.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
library(viridis)
library(lubridate)
library(switchgrassGWAS)
library(GGally)
library(maps)
library(ggmap)
usa <- map_data("usa")
source("~/Github/Functions_ggplot-theme-adjustments_2018-01-03.R")
```

# Load data
Add any data that needs to be loaded for these analyses here.
```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
metadata <- read_rds(file.path(workingdir, "data", "metadata.rds"))
sites <- read_rds(file.path(workingdir, "data", "sites.rds"))
subpops <- read_rds(file.path(workingdir, "data", "subpop_color_coding.rds"))
phe_gr_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_GR50.rds"))
phe_fl_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_FL50.rds"))
phenotypes <- readRDS("~/Github/pvdiv-phenology-gxe/data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
h2gr <- read_csv(file.path(workingdir, "analysis", "heritability", "kinship_subpop", "h2_df_GR50_related_functions_of_weather_v1.csv"))
h2fl <- read_csv(file.path(workingdir, "analysis", "heritability", "kinship_subpop", "h2_df_FL50_related_functions_of_weather_v1.csv"))
h2gr_gxe <- read_csv(file.path(workingdir, "analysis", "heritability", "kinship_subpop", "gxe_and_h2_df_GR50_related_functions_of_weather_v1.csv"))
h2fl_gxe <- read_csv(file.path(workingdir, "analysis", "heritability", "kinship_subpop", "gxe_and_h2_df_FL50_related_functions_of_weather_v1.csv"))

h2gr <- h2gr %>%
  full_join(h2gr_gxe)
h2fl <- h2fl %>%
  full_join(h2fl_gxe)
```
### older files to load
h2fl <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_FL50_related_functions_of_weather_v3.csv")
h2gr <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_GR50_related_functions_of_weather_v2.csv")
h2gr4 <- read_csv(file.path(workingdir, "analysis", "heritability", "h2_df_GR50_related_functions_of_weather_v4.csv"))
h2gr <- h2gr %>%
  full_join(h2gr4)

@@

# Map Fig 1A

```{r}
subpops
library(ggrepel)

metaplot <- metadata %>%
  filter(SUBPOP %in% c("Gulf", "Midwest") & !is.na(LATITUDE)) %>%
  mutate(LONGITUDE = -LONGITUDE)
metaplot$ECOTYPE_NNET <- factor(metaplot$ECOTYPE_NNET, levels = c("Coastal", "Lowland", "Upland", "Unknown"))
siteplot <- sites %>%
  filter(!(SITE %in% c("FRMI", "OVTN")))

ggplot() + 
  geom_polygon(data = usa, aes(x=long, y = lat, group = group), 
               fill = "white", color = "black") +
  coord_quickmap(xlim = c(-105, -66), ylim = c(25, 50)) +
  geom_jitter(data = metaplot, aes(x = LONGITUDE, y = LATITUDE, 
                                   color = SUBPOP, shape = ECOTYPE_NNET),
              width = 0.45, height = 0.45) + 
  geom_point(data = siteplot, aes(x = Longitude, y = Latitude), shape = 21, size = 4, stroke = 1.5, fill = "white") +
  geom_point(data = siteplot, aes(x = Longitude, y = Latitude), shape = 4, size = 3, stroke = 1.5) +
  geom_label_repel(data = siteplot, aes(x = Longitude, y = Latitude, label = manu_site), alpha = 0.7) +
  labs(x = "Longitude", y = "Latitude") + 
  theme(legend.position = "right") +
  scale_color_manual(values = c("#F47F72", "#442C83")) +
  scale_shape_manual(values = c(0, 6, 1, 4)) 
  #scale_fill_manual(values = c("#280B54FF","#FAC127FF", "#D44842FF", "white")) +
  #scale_color_manual(values = c(rep("black", 10), "#280B54FF","#FAC127FF", "#D44842FF", "white", "#280B54FF","#FAC127FF", "#D44842FF", "white"), guide = FALSE) +
  #scale_alpha_manual(values = c(0.7, 0.7, 0.7, 0.7), guide = FALSE)
save_plot(filename = "../manuscript/plots/Map_subpops_and_Ecotypes.png", plot = last_plot(), base_height = 3)
?geom_point
```

# -- Figure 1 B
# Phenotype correlations
can you easily look at the correlation between greenup ranks at OK versus NE?
```{r}
phe_gr_df %>%
  filter(SITE %in% c("LINC", "STIL")) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, -PLOT_GL) %>%
  pivot_wider(names_from = "SITE", values_from = "GR50", values_fn = mean) %>%
  ggplot(aes(x = STIL, y = LINC)) +
  geom_hex() + #aes(color = SUBPOP), height = 1, width = 1) +
  scale_fill_viridis(option = "B",
                     end = 0.9, direction = -1)

@@

```{r}
pand <- cor_fl %>%
  filter(SUBPOP %in% c("Gulf")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
pane <- cor_fl %>%
  filter(SUBPOP %in% c("Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
panf <- cor_fl %>%
  filter(SUBPOP %in% c("Gulf", "Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
pana <- cor_gr %>%
  filter(SUBPOP %in% c("Gulf")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = c(0.4, 0.85))
panb <- cor_gr %>%
  filter(SUBPOP %in% c("Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
panc <- cor_gr %>%
  filter(SUBPOP %in% c("Gulf", "Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")

pheno_corr <- plot_grid(pana, panb, panc, pand, pane, panf, nrow = 2)
save_plot(filename = "../manuscript/plots/Phenotypic_correlations_GR50_FL50_2.svg", plot = pheno_corr, base_width = 6.5)
```

# --- Fig 1 C & D
# Heritability Plots

Within common gardens, h2 were typically quite high: 62% on average for greenup date, and 87% for flowering date. However, h2 were not consistently high, notably for greenup at our OK and NE common gardens.
```{r}
h2all <- h2fl %>%
  full_join(h2gr)

h2all %>%
  filter(phe %in% c("FL50", "GR50") & site %in% c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD")) %>%
  group_by(phe) %>%
  summarise(meanh2 = mean(Estimate))

h2all %>%
  filter(phe %in% c("FL50", "GR50") & site %in% c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD")) %>%
  filter(Estimate < 0.2)

h2all %>%
  filter(phe %in% c("FL50", "GR50") & site %in% c("eight_sites")) %>%
  group_by(phe) %>%
  summarise(meanh2 = mean(Estimate))

h2all %>%
  filter(phe %in% c("GR50") & site %in% c("tx_sites", "north_sites")) %>%
  mutate(GandGxE = Estimate + GxE_Estimate) %>%
  select(GandGxE, Estimate:phe, GxE_Estimate) %>%
  group_by(site) %>%
  summarise(meanh2 = mean(Estimate + GxE_Estimate))

h2all %>%
  filter(site %in% c("eight_sites")) %>%
  mutate(GandGxE = Estimate + GxE_Estimate)  %>%
  select(GandGxE, site:phe, Estimate, GxE_Estimate)
```

## h2 as functions of GR50 and FL50
```{r}
h2all <- h2fl %>%
  full_join(h2gr)
unique(h2all$site)
f1h2 <- h2all %>%
  filter(phe %in% c("FL50", "GR50")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          site == "tx_sites" ~ "Texas",
                          site == "north_sites" ~ "North",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "GR50" ~ "50% greenup",
                              phe == "FL50" ~ "50% flowering",
                              TRUE ~ phe))
f1h2$site <- factor(f1h2$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All"))#, "Texas", "North"))
f1h2$phe_name <- factor(f1h2$phe_name, levels = c("50% greenup", "50% flowering"))
f1h2$subpop_name <- factor(f1h2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
ggh21 <- f1h2 %>%
  filter(!(site %in% c("nine_sites", "IL")) & !is.na(subpop_name) & !is.na(phe_name) & !is.na(site)) %>%
  ggplot(aes(x = site, y = Estimate)) +
  geom_bar(aes(fill = site %in% c("All", "Texas", "North")), stat = "identity") +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(phe_name ~ subpop_name) +
  theme(panel.spacing.x = unit(0.1, 'cm'), 
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none") + 
  ylim(c(0, 1)) +
  xlab("Common Gardens") + 
  ylab(bquote('h'^2)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
  #
save_plot("../manuscript/plots/h2_GR_FL_site_by_subpop_k_specific.png", plot = ggh21, base_width = 5.5, base_height = 3)
```

## h2 flowering weather
```{r}
flh2 <- h2fl %>%
  filter(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          site == "tx_sites" ~ "Texas",
                          site == "north_sites" ~ "North",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "FL50" ~ "50% flowering",
                              phe == "dyln_fl50" ~ "daylength",
                              phe == "dyln_change_sec" ~ "daylength change (s)",
                              phe == "cgdd_12c_gr2fl" ~ "GDD, GR to FL",
                              phe == "crain_gr2fl" ~ "Rainfall, GR to FL",
                              phe == "crain_1d" ~ "Rainfall, 1 day",
                              phe == "crain_2d" ~ "Rainfall, 2d sum",
                              phe == "crain_3d" ~ "Rainfall, 3d sum",
                              phe == "crain_5d" ~ "Rainfall, 5d sum",
                              phe == "crain_7d" ~ "Rainfall, 7d sum",
                              TRUE ~ phe))
flh2$site <- factor(flh2$site, levels = rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North")))
flh2$phe_name <- factor(flh2$phe_name, levels = c("50% flowering", "daylength",
                                                  "daylength change (s)",
                                                  "GDD, GR to FL",
                                                  "Rainfall, GR to FL",
                                                  "Rainfall, 1 day",
                                                  #"Rainfall, 2d sum",
                                                  "Rainfall, 3d sum",
                                                  "Rainfall, 5d sum"#,
                                                  #"Rainfall, 7d sum"
                                                  ))
flh2$subpop_name <- factor(flh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
site_plot <- rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD", "All", "Texas", "North"))
subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))

save_plot("../manuscript/plots/h2_FL_site_weather_functions_single_sites_k_specific.png", plot = flh2_p1, base_height = 7, base_asp = 1.1)

flh2_p2 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.8)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")

save_plot("../manuscript/plots/h2_FL_site_weather_functions_site_groups_k_specific.png", plot = flh2_p2, base_height = 4, base_asp = 1.5)

site_plot <- c("All")

flh2_p3 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.5)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")
save_plot("../manuscript/plots/h2_FL_site_weather_functions_All_Sites_k_specific.png", plot = flh2_p3, base_height = 3.5)
```
## gxe flowering all, north, texas
```{r}
site_plot <- c("All", "Texas", "North")
